---
title: "lab02"
author: "Xiaobing Xu"
date: "4/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(knitr)
```

```{r}
yrbs <- read.delim("../Data/all-data/yrbs.tsv.bz2")
yrbs %>%
  head()
```
##### Identifying Assumptions
1.The assumption for DID combines both the cross-sectional and before-after estimators, which compares treated-nontreated differences before and after the treatment. In other words, we will test both the treated group and non treated group of before and after the campagin in meth use. 

2. I think it might plausible since there is difference and gap for the treated and non treated group before and after the compaign.

```{r}
yrbs$T <- yrbs$year < 2006
head(yrbs)
```

```{r}
yrbs <- yrbs %>%
  rename(A = state)
head(yrbs)
```

```{r}
table <- yrbs %>% 
  group_by(A, T) %>%
  summarize(avg_meth_use = mean(meth))
kable(table)
```

##### 2.3 Run a regression with full controls

```{r}
did_r <- lm(meth ~ A * T, data = yrbs)
summary(did_r)
```

##### 2.4 Run a regression with full controls

```{r}
yrbs$before <- yrbs$year < 2006
did_r2 <- lm(meth ~ A * T * age * sex * tv, data = yrbs)
summary(did_r2)
```

The results shows a great significance in meth usage since the p-value is less than 0.05 which is statistically significant for the treatment group and after the treatment variables when they crossed. Meanwhile, I consider this number credible which corresponds with my identifying assumption which is plausible too. The treated and non-treated groups shows difference before and after the campaign.




