---
title: "Lab01-ba-cs"
author: "Xiaobing Xu"
date: "4/5/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

## 1 Was Montana Meth Prevention Project Effective?

## Load data 

```{r}
data1 <- read.delim("../Data/all-data/yrbs.tsv.bz2")
data1 %>%
  head()
```
1.2
The treatment is tvcom, the outcome is meth use

```{r}
data1 <- data1 %>%
  mutate(after = (year >= 2006) + 0)
data1 %>%
  head()
```

1.3
```{r}
result <- data1 %>%
  filter(year >= 2006) %>%
  group_by(state) %>%
  summarize(mean(meth))
result
result[1,2] - result[2,2]
```

1.4
We only need post-project data because we are analyzing whether this project had effect on children.

```{r}
lm(meth ~ state, data=data1, subset = (after == 1)) %>%
  summary()
```
1.6
In this approach, we can easily identify through means that the average meth use for Montana is less than the national level by **0.00181**. A t value of 0.592 shows that *state* is not very significant. Montana has a lower estimate of meth usage than National by **0.00181**, very similar to the first approach. 


1.7
The assumption is that explained and explanatory variables dealing with the same single period of point in time.

2.1
```{r}
result2 <- data1 %>%
  filter(state == 'MT') %>%
  group_by(after) %>%
  summarize(mean(meth))
result2
```
2.2
```{r}
yrbs2 <- data1 %>%
  filter(state == 'MT')
lm(meth ~ I(year >= 2006), data=yrbs2) %>%
  summary()
```

2.3
It is statistically significant since p-value is too small, which is smaller than 0.01 and 0.05.  A t value of 8.225 shows that this is very significant. After the program has a lower estimate of meth usage than before the program by **0.038619**. We see similarly that after the program has a lower estimate than before by **0.038590**, and another significant variable is age, with a t value of 4.953.

2.4
It deadling with different period of time based on one point.

2.5
I believe the second approach is more convincing since the second approach gives us more insight to how significant the *before* variable is.
